Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-12-04 prop_letter_ajhs.tex
From: Hanson, Andrew J. Sent: Monday, December 04, 2017 1:18 To: Tai, Yu-Tsung <yuttai@indiana.edu> Cc: Hanson, Andrew J. <hansona@indiana.edu>; Ortiz, Gerardo <ortizg@indiana.edu>; Sabry, Amr A. <sabry@indiana.edu> Subject: #3 corrected. RE: AJH typo corrections and separate major suggested edits: re: AL11679 Tai
Hi -  missed that - the "**" meant it was copied and I was supposed to
edit it and erase the "**": Here is the correct #3, which my be too
simple, but it seemed to me that the thought of the last paragraph at
the bottom of p2/top of p3 was written backwards, and could be made
clearer

%% ajh: Inverted logic: LONG SUGGESTED 
\andy{TEXT \#3 would go here}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
\andy{End of TEXT \#3}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

>>>>

%% ajh: Inverted logic: LONG SUGGESTED 
\andy{TEXT \#3 would go here}
If all the conditions are satisfied, and one knows all the
  $\ket{\phi_j} = \sum_{k=1}^{d}\alpha_{k}\ket{k}$ representing
the current state $\rho$ of the quantum system, then a conventional
probability measure can easily be
constructed~\citep{Born1983bibTeX,Mermin2007,Jaeger2007},  taking the 
form
\[ \muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}  q_{j}\muB_{\phi_{j}}\left(P\right) \ . \]
\andy{End of TEXT \#3}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
